---
title: "Fighting The Frame: How Framing Police Brutality Influences Blame"
author: 
  - name: Kade Davis
    affil: 1
  - name: Nathan Alexander, PhD
    affil: 2, 3
affiliation:
  - num: 1
    address: Department of Sociology, Morehouse College
  - num: 2
    address: Department of Curriculum and Instruction, Howard University
  - num: 3
    address: Program in Applied Data Science and Analytics, Howard University
column_numbers: 3
logoright_name: img/hu-logo.jpg
logoleft_name: img/morehouse-logo.jpg
titlebox_borderwidth: "0.35cm"
primary_colour: "#ffffff"
secondary_colour: "#5F6062"
accent_colour: "#E51937"
titlebox_bordercol: "#840028"
title_textcol: "#840028"
author_textcol: "#840028"
affiliation_textcol: "#840028"
columnline_col: "#000000"
columnline_style: solid
sectitle_textcol: "#ffffff"
sectitle_bgcol: "#840028"
sectitle_bordercol: "#840028"
sectitle2_textcol: "#840028"
output: 
  - posterdown::posterdown_html
bibliography: references.bib
---

```{r setup, include=FALSE}
# setwd("C:/Users/kadej/Dropbox/sonya.quanteda")
# getwd()
knitr::opts_chunk$set(echo = TRUE, fig.width = 12, fig.height = 8)
#install.packages("pak")
#install.packages("posterdown")
#pak::pak('rstudio/pagedown')
library(readr)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(scales) # For formatting axis labels
library(here)
library(pdftools)
library(quanteda)
library(readtext)
library(stringr)
library(rvest)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(tidycensus)
library(dplyr)
library(quanteda.textmodels)
library(ggplot2)
library(sf)
library(viridis)
library(mapview)
library(maps)
library(quanteda.textplots)
library(quanteda.textstats)
library(fs)
here::i_am("frame_poster.Rmd") # if you change the name of your file, update this
```

```{r, eval=FALSE, include=FALSE}
# do not remove; this line is to create the PDF version of your poster
pagedown::chrome_print("frame_poster.Rmd")
```


# Overview

This study explores Snow’s Theory of Framing and Tilly’s Theory of Blame by answering the question: *How does the framing of police brutality in legacy news articles relate to the way commenters assign blame to groups and individuals involved?* This study uses articles produced by legacy news sources regarding Sonya Massey, a Black woman in Springfield, Illinois, shot in her home by two police officers over a dispute regarding a pot of boiling water. Exploratory semantic analysis is used to analyze measures between themes within a subset of news articles and their comments. Semantic measures are compared to examine discuss framing and influence. 

# Literature Review

Media and sociology scholars approach the concept of framing from differing perspectives but both find that framing significantly affects the lives of those who are framed. This study will reinforce the use of Snow’s framing perspective in combination with Tilly’s blame process by highlighting the interdisciplinary relevance of the subjects.

## Snow’s Theory of Framing

Please add notes about Snow's Theory of Framing.

## Tilly’s Theory of Blame

Tilly agrees with this argument positing that blame is a key factor in establishing social movements [@Roberge2009]. Many sociologists support Tilly’s claim that blame plays a heavy role in contributing to the effects of framing and acknowledge its connection to Blame. However, few ground the connection in empirical evidence and focus too heavily on the framing aspect of the study, neglecting the role of blame.

---

# Data and Method

This study will analyze legacy news source articles about Sonya Massey. Articles will be gathered from legacy news websites. Legacy news sources have a large following, consistent reliability with experienced editors, and less biased reports than non-legacy sources (@Diel2017). I have chosen to analyze articles about Sonya Massey because she has been one of the most recent and prominent cases of police brutality and has much coverage on social media. This study uses 12 articles from the legacy news sources New York Times, ABC, NBC, Washington Post, Fox News, and CNN. 

## Data

There will be two articles from each news source. “Article 1” will be the oldest article addressing Sonya Massey, and the “Article 2” will be the article directly after the oldest article. This study addresses the first question by finding the frequency of the words in the articles and comments that refer to the themes "Police" or "Massey." The frequency of these themes (measured by the word count)  in the articles are correlated to the themes present within the corresponding article’s comments. There will be a correlational comparison between “article 1” and “article 2” to explore effects of introducing new information. Both will be tested using a chi-square fitness of goodness test. 

## Method

```{r}
library(ggplot2)
library(quanteda.textplots)

analysis_dir <- "./data/analysis_objects"

if(!dir_exists(analysis_dir)) {
  dir_create(analysis_dir)
  stop(
    "Analysis directory created at ", analysis_dir, 
    "\nPlease run your analysis pipeline to generate objects."
  )
}

load_analysis_object <- function(object_name) {
  file_path <- path(analysis_dir, paste0(object_name, ".rds"))
  
  if(!file_exists(file_path)) {
    stop("File not found: ", file_path, 
         "\nAvailable files: ", paste(dir_ls(analysis_dir), collapse = "\n"))
  }
  
  tryCatch(
    readRDS(file_path),
    error = function(e) {
      stop("Failed to load ", object_name, ": ", e$message)
    }
  )
}
```

```{r, echo=F, warning=F, messages=F}
tokens_obj <- load_analysis_object("tokens")
top_features <- load_analysis_object("top_features")
doc_corpus <- load_analysis_object("corpus")


```

```{r, include=F}
# 1. TOP FEATURES VISUALIZATION -------------------------------------------
top_features_df <- data.frame(
  Term = names(top_features),
  Frequency = unname(top_features)
)
```

```{r, echo=F, messages=F, warning=F}
ggplot(top_features_df, aes(x = Frequency, y = reorder(Term, Frequency))) +
  geom_col(fill = "steelblue") +
  labs(
    title = "Top 20 Features in Sonya Massey Coverage",
    x = "Frequency",
    y = "Term"
  ) +
  theme_minimal()
```

```{r, include=F}
# 2. SOURCE DISTRIBUTION -------------------------------------------------
docvars(doc_corpus) %>%
  count(source) %>%
  ggplot(aes(x = source, y = n)) +
  geom_bar(stat = "identity", fill = "darkorange") +
  labs(
    title = "Document Distribution by Source",
    x = "News Source",
    y = "Count"
  ) +
  coord_flip()
```

```{r, echo=F}
# 3. WORDCLOUD -----------------------------------------------------------
set.seed(123)
textplot_wordcloud(
  dfm(tokens_obj),
  min_count = 5,
  color = c("steelblue", "darkorange", "firebrick")
)

# 4. TYPE COMPARISON -----------------------------------------------------
tokens_by_type <- dfm_group(dfm(tokens_obj), groups = type)
```

```{r, echo=F}
textplot_keyness(
  textstat_keyness(tokens_by_type, target = "news_article"),
  show_legend = FALSE
) +
  labs(title = "Keyness Analysis: News Articles vs User Comments")
```


# Findings

# Discussion

# Conclusion

Framing has been a prevalent subject within contemporary society, and many scholars have explored its effects on news media. Sociologists, in particular, have made great contributions to the concept; however, there is a significant lack of literature regarding the framing of police brutality in the news. This study explores how the framing of police brutality by legacy news sources affects how the audience assigns blame using semantic analysis to analyze a correlation between themes within articles and their comments.

# Acknowledgements

# References